SEDONA: A Novel Protocol for Identifying Infrequent, Long-Running Daemons on a Linux System

### 2017-02-02 sedona-ieice16/revision/paper.tex
SEDONA updates

We used 128~seconds as the task length and ran the PUT program (termed PUT128) 
800~times. Fig.~\ref{fig:meas_comp} shows two histograms of the timing results on PUT128.
Most of the 800 executions measured in elapsed time, 
via  {\tt System.currentTimeMillis()} in Java, are gathered in the tallest bar 
of \hbox{128,000--129,000 msec,} with just a few executions outside of that bar, as can be seen in Fig.~\ref{fig:hist_before_et}. 
But these outliers significantly impact the overall measurement quality: 
a standard deviation of 1,700 msec and a relative error of 0.03. 
\shorten{This result suggests adequately eliminating these outliers 
while retaining most of the measured executions.}

In contrast, our scheme, which we propose shortly, 
significantly reduces such variability.
The gist of the scheme is to (i)~focus on
{\em process time} (PT) rather than on elapsed time (ET) and 
(ii)~remove some executions that involve
{\em infrequent, \hbox{long-running} daemon processes}, which impact
the process time of the process. 
Using PT is preferred, in that it considers 
the time taken for only a process of interest.
PT can be calculated as the sum of ticks (where one tick is equal to 10 msec)
in user and system mode, available via {\tt taskstats} C struct, 
provided by the Linux NetLink facility~\cite{Netlink}.
This use of PT and selective elimination 
was able to improve 
measurement quality---in both standard deviation and relative error---up to by 
three orders of magnitude for PUT128, as illustrated in Fig.~\ref{fig:hist_after_pt}.

>>>>

We used 128~seconds as the task length and ran the PUT program (termed PUT128) 
800~times. 
%Fig.~\ref{fig:meas_comp} shows two histograms of the timing results on PUT128.
{\color{blue}Fig.~\ref{fig:meas_comp} shows two plots of the timing results on PUT128.
%Most of the 800 repetitions measured in elapsed time, 
%via  {\tt System.currentTimeMillis()} in Java, are gathered in the tallest bar 
%of \hbox{128,000--129,000 msec,} with just a few executions outside of that bar, 
%as can be seen in Fig.~\ref{fig:hist_before_et}. 
Most of the 800 repetitions measured in elapsed time, 
via  {\tt System.currentTimeMillis()} in Java, form the central band 
of \hbox{128,000--129,000 ms,} as can be seen in Fig.~\ref{fig:hist_before_et}. 
There also exist over a dozen of repetitions above that band, called outliers.
But these outliers {\em critically} impact the overall measurement quality: 
a standard deviation of 1,730 ms and a relative error of 0.01.
This result suggests adequately eliminating these outliers 
while retaining most of the measured executions.}

{\color{blue}
Our protocol, which we propose shortly, on the contrary, 
effectively identifies and removes those outliers. 
In effect, the protocol considerably reduces such variability.
The protocol identified and removed fifteen repetitions 
that had {\em infrequent, \hbox{long-running} daemon processes}, 
impacting the execution time of PUT128. 
In addition, the protocol utilized {\em process time} (PT) (of PUT128) 
rather than elapsed time (ET). 
Using PT is preferred, in that it considers 
the time taken for only a process of interest.
PT can be calculated as the sum of ticks (where one tick is equal to 10 msec)
in user and system mode, available via {\tt taskstats} C struct, 
provided by the Linux NetLink facility~\cite{Netlink}.
As a result, none of the retained timing results was outside of 
the central band in Fig.~\ref{fig:hist_after_pt}, and thus 
the measurement quality---in both standard deviation and relative error---was 
improved up to by three orders of magnitude for PUT128, 
as shown in Fig.~\ref{fig:hist_after_pt}.
}

%The key idea to the protocol is to (i)~utilize
%{\em process time} (PT) rather than on elapsed time (ET) and 
%(ii)~throw out some executions that involve
%{\em infrequent, \hbox{long-running} daemon processes}, which impact
%the process time of the process. 
%Using PT is preferred, in that it considers 
%the time taken for only a process of interest.
%PT can be calculated as the sum of ticks (where one tick is equal to 10 msec)
%in user and system mode, available via {\tt taskstats} C struct, 
%provided by the Linux NetLink facility~\cite{Netlink}.
%This use of PT and selective elimination 
%was able to improve 
%measurement quality---in both standard deviation and relative error---up to by 
%three orders of magnitude for PUT128, as illustrated in Fig.~\ref{fig:hist_after_pt}. 
%}
